### 2016-11-05 introduction.tex
more shit

Essentially, \cite{mozer1989using} observed that neural networks during training do \textit{not} distribute the learning representation evenly or equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units must learn a complex interdependence function which cancels out their respective influence on the network output. Furthermore, assuming enough units exist to learn the function in question, increasing the number of parameters does not increase the richness or robustness of the learned approximation, but rather simply increases the number of noisy parameters to be canceled during training. This is evinced by the fact that in many cases, multiple neurons can be removed from a network with no re-training and with negligible impact on the quality of the output approximation. In other words, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is true, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning can be viewed as a necessary treatment procedure to ``trim the fat.''

We observed copious evidence of this phenomenon in our experiments, and this is the motivation behind our decision to evaluate our pruning algorithms on the simple criteria of their ability to trim neurons \textit{without} any re-training. If we were to employ re-training as part of our evaluation criteria, we would arguably \textit{not} be evaluating the quality of our algorithm's pruning decisions per se but rather the ability of back-propagation trained networks to recover from faults caused by non-ideal pruning decisions, as suggested by the conclusions of \cite{segee1991fault} and \cite{mozer1989skeletonization}. Moreover, as \cite{fahlman1989cascade} discuss, the ``herd effect'' and ``moving target'' phenomena in back-propagation learning will simply cause the remaining units in a network to shift course to account for whatever error signal is re-introduced as a result of a bad pruning decision or network fault. So long as there are enough critical parameters to learn the function in question, a network can almost always recover with additional training. This limits the conclusions we can draw about the quality of our pruning criteria.

>>>>

Essentially, \cite{mozer1989using} observed that neural networks during training do \textit{not} distribute the learning representation evenly or equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units must learn a complex interdependence function which cancels out their respective influence on the network output. Furthermore, assuming enough units exist to learn the function in question, increasing the number of parameters does not increase the richness or robustness of the learned approximation, but rather simply increases the number of noisy parameters to be canceled during training. This is evinced by the fact that in many cases, multiple neurons can be removed from a network with no re-training and with negligible impact on the quality of the output approximation. In other words, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is the case, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning can be viewed as a necessary treatment procedure to ``trim the fat.''

We observed copious evidence of this phenomenon in our experiments, and this is the motivation behind our decision to evaluate our pruning algorithms on the simple criteria of their ability to trim neurons \textit{without} any re-training. If we were to employ re-training as part of our evaluation criteria, we would arguably \textit{not} be evaluating the quality of our algorithm's pruning decisions per se but rather the ability of back-propagation trained networks to recover from faults caused by non-ideal pruning decisions, as suggested by the conclusions of \cite{segee1991fault} and \cite{mozer1989skeletonization}. Moreover, as \cite{fahlman1989cascade} discuss, the ``herd effect'' and ``moving target'' phenomena in back-propagation learning will simply cause the remaining units in a network to shift course to account for whatever error signal is re-introduced as a result of a bad pruning decision or network fault. So long as there are enough critical parameters to learn the function in question, a network can almost always recover with additional training. This limits the conclusions we can draw about the quality of our pruning criteria when we employ re-training.
